\chapter{Functional Specifications} \label{spec}
This chapter describes the functional specifications of a system for settlement in a microgrid. The specifications are divided into three categories: application from the user's perspective; application from computer's perspective; and the blockchain.

Each node consists of a smart meter%ams (automatic electricity meter)
 for registering consumption and production of electricity. The smart meter is connected to the node's computer. The computer receives data from the smart meter and processes the data before passing it on to the blockchain, which also runs on the computer. Nodes are uniquely identified by their ID.  

The system consists of the following participants:

\begin{itemize}
\item Consumers purchasing electricity.
\item Prosumers who consume electricity, and sell excess electricity from their own production. Prosumers can also purchase electricity from others.
\item Public producers delivering electricity on demand through generators, batteries, or power transmitting cables. 
\end{itemize}

Having power delivered by public producers is a costly solution, and should be avoided. Participants can be discouraged from this solution by setting extreme prices on electricity from these sources.
%SCALABILITY
\section{User Interface} \label{user}
This section describes how the user interacts with the system.

\begin{enumerate}
\item Users connect to existing nodes on the Network, given an IP address and a port number. The user also chooses a port to run the application on. 
\item A website lets users set up smart contracts and tracks their energy flow. 
\item The website requires a login where users are identified by their node ID. 
\item Prosumers with surplus electricity to sell, put up their availability on the website.
\item Consumers who want to purchase electricity can query available producers and initiate a smart contract.
\item Users can monitor how much electricity they produce and consume in real-time.
\end{enumerate}

%Tilkoling av målinger - 
%alt som går inn og ut - hva og hensikt - er det funksjonelle 

\subsection{Use Case}
Use cases for how prosumers and consumers interact with the system are described below.
\subsubsection*{Prosumer}
A user who produces excess electricity can choose to sell this electricity to neighbors connected to the microgrid. The user connects to the network grid and is given a unique public/private key pair, which is the node ID and a corresponding password. The user can log in to the website and advertise the available electricity to other users on the network. When queried by consumers about availability, the users can set up a smart contract. The user can log in to the website and monitor how much electricity they consume, and how much they produce to the grid, as well as the electricity price. If a prosumer does not meet the requirements of a contract, he or she must pay a fee corresponding to the difference between the price the prosumer is selling at, and the price of available energy.

%Differansen batteri/generator

\subsubsection*{Consumer}
Users wishing to purchase electricity from their neighbors can connect to the microgrid network. After logging in to the website with their given node ID and password, they can query other users for available electricity. The consumer can set up a smart contract with a prosumer. Consumers can at any time log in to the website and monitor how much electricity they consume at minute intervals, and at what price. If the consumer decides to use less energy than what was specified in the contract, he or she must pay a fee corresponding to what the producer is losing in profit.


\section{Application Interface} \label{computer}
This section describes how the computer handles incoming data from the users and connected smart meters, forwarding the data to the blockchain, and settling the transaction between users.
\begin{enumerate}
\item The computer is connected to a smart meter and receives information about a node's consumption and production of electricity at periodic intervals. 
\item The machine passes the readings on to the blockchain for storage. 
\item When two users initiate a smart contract, the machine passes it on to the blockchain for validation and storage.
\item New readings from the smart meter are processed on the website and added to the graphs for consumption and production.
\item Settlement is done every time new readings occur. Based on valid contracts in the system and data from the readings, each node's bill is updated reflecting the latest transactions.
\end{enumerate}

\subsection{Use Case}
Following are use cases for when the computer receives a new meter reading, how consumption and production of electricity are monitored, and how smart contracts are processed. 
\subsubsection*{New Meter Reading}
Once, every minute, the computer receives measurement readings from the smart meter. The readings include the node ID of the smart meter, and amount of electricity produced and consumed since the last reading. The information is then passed on to the node's blockchain for storage. The settlement module in the applications settles the new readings based on the valid contracts in the system. 

\subsubsection*{Monitoring Consumption and Production}
When new measurements are received from the smart meter, the readings become available to the user through the monitoring display on the user interface. A super user can view graphs for all nodes in the network. Individual nodes can only see their own graph, by logging in with the node ID.

\subsubsection*{New Contract}
When two users initiate a contract through the user interface on the web site, it is passed to the blockchain for validation and storage. When new meter readings are registered, the system iterates through valid contracts to settle the new transactions

\section{Blockchain} \label{blockspec}
The blockchain acts as the back-end service to support the requirements given in sections \ref{computer} and \ref{user}.
\begin{enumerate}
\item The application sends two types of input to the blockchains, a smart contract between two users and electricity transactions. There are two types of blockchains. One for storing smart contracts, and one for storing electricity transactions.
\item The blockchains are distributed between all the nodes in the network. 
\item The nodes broadcast their individual transactions across the network, while new smart contracts are sent directly to the consensus leader.
\item The leader of the blockchain proposes a new blocks when data is available.
\item The proposed block is broadcasted to the consensus nodes, who validate the block and the transactions.
\item If a majority of the nodes deem the block valid, all nodes will add the new block to their blockchain.
\item When the application is settling new transactions, valid smart contracts in the blockchain are triggered and used in the settlement process. 
\end{enumerate}

\subsection{Use Case}
How the blockchain handles smart contracts and electricity transactions are described in the use cases below.
\subsubsection*{Smart Contract}
When two users decide to initiate a smart contract, it is sent to the blockchain for validation. The users sign the contract with a digital signature - their private key. The signature can later be verified with the user's public key.
When the smart contract is passed to the blockchain module, it is added to a block and verified by the nodes before the block is stored in the blockchain.
 
\subsubsection*{Electricity Transactions}
New electricity transactions from all network nodes are passed to the blockchain layer every minute. New transactions from each node are broadcasted throughout the network. The current leader adds all new transactions to a block, which is validated by the nodes before it is stored in the blockchain. 


%\section{Technical Specifications}

%The implementation of this system is focused around the software; the hardware is out of scope. The actual transfer of energy, including transmission lines; utility readings; and other hardware, is not part of the scope either. It is assumed that one or more computers exist that can monitor the microgrid and the energy flow to and from a node, as well as running a virtual machine for validation of blocks, creation and execution of smart contracts, and running and monitoring the blockchain. For the purpose of this project, these features will be simulated.

%Each node in the system consists of a server and several clients connected to the servers. Since the microgrid will only have a finite number of participants, all nodes are connected to each other. Messages are either broadcasted or sent to specific nodes in the system. 
%The types of messages in the system includes, but are not limited to, initial discovery of new nodes; initial synchronization of the blockchain; broadcasting new transaction; proposing new blocks; consensus voting on new blocks; 

%Following are the technical specifications of the system.


%This chapter contains the specifications for the system to be implemented. 
%\subsection{Blockchain Specification}
%The blockchain will be permissioned, where nodes connect to network by obtaining information from other nodes already on the network. The blockchain will not be completely private, but rather a consortium where all the nodes allowed access to the network are participating in the validation of new blocks. 

%(An alternative approach for accepting new nodes in to the network, is to make it part of the consensus model. For instance, say the network is started by an initial group of nodes. If a new node is to be introduced into the network, M of N nodes must validate the node before it can enter the network. This could work in a system such as a microgrid, where participants are physically close, possibly acquaintances in real life, and the system is finite. Key distribution would then be handled differently e.g. by a key generating function. This potentially provides higher user privacy, which might not be ideal in such a system.)

%Blocks are created every minute, and will contain all in-going and out-going electricity for the past block interval. Blocks may also contain smart contracts entered by two users in the network. Blocks must be approved by the network majority before they are added to the blockchain.
%Each block/transaction contains a timestamp to help prevent double spending of tokens or double selling of electricity(?)%TODO

%The Raft consensus algorithm is used where the majority of the nodes must validate a block before it is commited. As previously mentioned, all nodes in the network participate in the consensus process of validating new blocks. This is to prevent centralization of the blockchain. Since the blockchain is not public, there is no reason to rely on cryptoeconomics for incentives to keep the blockchain correct. The users have already been approved, so there is little to no risk of an attack. This consensus algorithm requires far less computing power than PoW (and PoS?) and can also be implemented to perform much faster transactions. %Uryddig No possibility of forks, as consensus is reached before commit

%\subsection{Smart Contract Specification}
%A consumer signs a contract with a producer/prosumer for a given amount of time, e.g. a month. The consumer can at any time decide how much electricity they want to buy, or if the want to buy anything at all. Fluctuations in price will likely influence this decision. Once a consumer signs a contract from one producer/prosumer, it cannot sign a new contract with someone else. However, it can opt out of using the electricity for a period by e.g. using a battery, or simply using less energy for a period of time, if it is expensive. This might help regulate pricing if it becomes too high due to high demands. 

%To ensure precise transactions of tokens/electricity, smart contract functionality is used. A consumer puts tokens into a contract with limitations on how much electricity they want to buy and at which prize. If current electricity price matches the limitations, the computing node (virtual machine) automatically "forwards" the right amount of energy to the right node, and the tokens in return. The contract locks the tokens until electricity has been consumed. In case of a prosumers/producers failure to provide electricity, tokens are transferred back to consumer. This functionality prevents double spending of tokens and double selling of electricity.

%The contracts will be stored in the blockchain, and automatically executed when the right conditions are met. A token contains a state indicating whether it is locked in a smart contract or not. An important reason for using smart contract functionality is that there are two assets being transferred in this system: tokens and electricity. In a cryptocurrency blockchain with only one asset, the sender of the asset initiates the transaction. As a result of the bi-directional transfer of assets, the smart contract is used to ensure that neither side can withdraw from the transaction when it is in progress. 


%



%Unlike bitcoin, there is no single asset that can be followed through out the blockchain. The asset of interest is electricity, which is not reusable. 

%No point in mining blocks, as there is no currency to create. Each participant in the network runs a virtual machine that takes care of validation of blocks, smart contracts, and monitors the blockchain. 

%Public/private cryptographic key that works as digital signatures in transactions. Also validates that electricity is sold/consumed by the right node. Public key also works as the address of that particular node.  

